\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% Multiple Columns
\usepackage{multicol}

% Page Margins (and size)
\usepackage[letterpaper, portrait, margin=1.5in]{geometry}

% No page numbering
\pagenumbering{gobble}

% New Drink Entry
\newcommand{\drink}[3]{
    \begin{center}
        \noindent\large \textbf{#1}\\
        \small \textit{#2}\\
        \normalsize #3\\
        \vspace{10 mm}
    \end{center}
}

\begin{document}
   \begin{center}
       \LARGE \textbf{Drink Menu} \\
       \small \textit{Jamie's House of Hrach} \\
       \hrulefill
   \end{center}

   \begin{multicols}{2}
   \drink{Planter's Punch}{Lime, Rum, Spices}{
         Spicy and delicious drunk juice to get any party started.
   }

   \drink{Rum \& Coke}{Rum, Coke, (Optional) Lime}{
      The goto for those not looking for adventure.
      Always dependable and there for you.
   }

   \drink{Tequila Sunrise}{Tequila, Orange, Cherry}{
      A drink truly made for summer. Fruity with a hint of cherry.
   }

   \drink{Screwdriver}{Vodka, Orange, (Optional) Peach}{
      A fruity take on drinking straight vodka. A college party staple.
   }

   \columnbreak

   \drink{Old Fashion}{Whiskey, Citrus}{
      A classy drink for the modern man. Cruise around town in style in your
      Lincoln town car.
   }

   \drink{Sex on the Beach}{Vodka, Fruity}{
      Matched only by Sex on the Beach. This girly drink won't get you laid
      but you might find yourself on a beach naked. Deceptively alcoholic.
   }

   \drink{Kamikaze}{Vodka, Citrus, Lime}{
      A drink for those who love citrus and lime. A new take on the classic sidecar.
   }

   \drink{Side Car}{Brandy, Citrus, Lemon}{
      This classic drink from 1910's will make you wish motorcycle sidecars
      were still a thing.

      Substitute Gin for White Lady.
   }

   \end{multicols}

   \vfill
   \begin{center}
      \noindent\textit{
          ``If you can't do your job drunk \\
          then you can't do your job.'' \\
          -- Will Orr's Boss
      }
   \end{center}

   \clearpage

   \begin{center}
      \LARGE \textbf{Shot Menu} \\
      \small \textit{Jamie's House of Hrach} \\
      \hrulefill
      \end{center}

      \drink{Blowjob}{Irish Cream, Amaretto or Coffee Liqueur}{
         Don't use your hands!!!
      }

      \drink{Jolly Rancher}{Vodka, Sour Apple}{
         Like it's namesake it's sweet, sour and oh so good.
      }

      \drink{Fireball}{Cinnamon Whiskey}{
         No party is complete without a round of Fireball shots!
      }

      \vfill
      \begin{center}

      \noindent\textit{
         ``If you can’t do your job drunk \\
            then you can’t do your job.'' \\
            -- Will Orr's Boss
      }
   \end{center}

\end{document}
